Comparative Analysis of Stream Processing Systems

### 2019-12-16 paper.tex

@@

\title{ Review of Stream Processing System }
\author{
    Shawn Zhong, Suyan Qu, Sulong Zhou \\
    \{wzhong36, squ27, szhou78\}@wisc.edu\\
    Group No. 7
}
\date{October 17, 2019}

@@

\subsubsection{Kafka Streams}
Kafka Streams is a real-time stream computing library that relies on existing Kafka clusters to provide distributed, highly fault-tolerant, real-time stream computation. Kafka Streams is designed to be lightweight. It has no external dependencies other than Kafka Stream Client library, ans can be easily embedded in Java applications.

>>>>

% https://arxiv.org/pdf/1709.01363.pdf

@@

\title{ Comparative Analysis of Stream Processing Systems }
\author{
    Shawn Zhong, Suyan Qu, Sulong Zhou \\
    \{wzhong36, squ27, szhou78\}@wisc.edu\\
    CS 744 Group No. 7
}
\date{October 17, 2019}

@@

\subsubsection{Kafka Streams}
Kafka Streams is a real-time stream computing library that relies on existing Kafka clusters to provide distributed, highly fault-tolerant, real-time stream computation. Kafka Streams is designed to be lightweight. It has no external dependencies other than Kafka Stream Client library, and can be easily embedded in Java applications.
